Single-cell RNA-sequencing reveals cellular dynamics of the developing mammary gland

### 2017-09-13 paper/main.tex
minor change

To further characterise the clusters, we identified differentially expressed genes and inferred putative identities based on known marker (\autoref{F2}a and b).
As shown in Table 1 multiple clusters of cells have been assigned to the same putative cell type.
We found that in these instances the cells showed a high similarity and expressed the same marker genes but derived from different developmental stages, suggesting that the stage of the gland has specific effects on the transcriptional landscape of certain cell types.\\

>>>>

To further characterise the clusters, we identified differentially expressed genes and inferred putative identities based on known marker (\autoref{F2}a and b).
As shown in Table 1 multiple clusters of cells have been assigned to the same putative cell type.
We found that in these instances the cells showed a high similarity and expressed the same marker genes but derived from different developmental stages (see NP, G, L or PI suffix in \autoref{F2}a), suggesting that the stage of the gland has specific effects on the transcriptional landscape of certain cell types.\\
